%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{acknowledgements}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}

\def\thanks#1{%
\begingroup
\leftskip1em
\noindent #1
\par
\endgroup
}

A few months back, I watched a video where former California governor and former bodybuilder Arnold Schwarzenegger delivered a speech at the graduation ceremony at the University of Huston a few years back. He said that the concept of a self-made man or woman is a myth. No one is truly self-made, as one's journey is supported by countless help and kindness. I could not agree with this statement more, which is why I would like to take some time to thank so many people for my unforgettable Ph.D. journey.


The most significant impact during my Ph.D. was made by my adviser Dr. Srdjan Capkun both professionally and personally. I can not thank him enough for his continuous support and guidance throughout the past years. He gave me immense freedom to explore the topics that I am truly passionate about. He guided me when I did not know what to do with that freedom. Srdjan has a unique mentoring skill, and the way he creates bonds with his students always amazes me. I tried to imitate some of his techniques while supervising students. The numerous discussion I had with him, not only about my work but also my personal life, had a profound effect on my perspective on science, and life, in general.


Another person who has a significant impact on my Ph.D. was Dr. Kari Kostiainen. He was not only a frequent collaborator, but also he mentored me towards formulating my ideas and giving me feedback on my writing.  Kari's structured way of writing papers had a visible impact on all my writings. I remember knocking on his office door on numerous occasions whenever I had some new ideas. Even though most of the ideas did not make it out of his office, some of our papers resulted from these frequent brainstorming sessions. I was always amazed to see no matter how heated the discussions were; he was always calm and composed.


Dr. Rahul Purandare, my master's thesis adviser at IIIT-Delhi, had a significant influence on me for shaping my career path. Not only he gave me an abundance of freedom to work on my idea, but he also encouraged me to pursue a research career and supported me enormously. Joining the Ph.D. program at ETH is something that was a result of his continuous encouragement. Similarly, Dr. Pinaki Sarkar, my bachelor thesis adviser, had an impact on shaping my very early, naive understanding of research. He took me under his wings to work beside him during his Ph.D. My fond memories of taking long walks with him to brainstorming combinatorics and cryptography are something I cherish. I learned a great deal about critically think about the problems, relentlessly working and shaping ideas, and scientific writing.


In 2016, during the time of changing continent and moving to Z\"urich, I was afraid that it would be a stressful affair given how far away I would be from my family and life-long friends. However, I was extremely fortunate to create bonds and had a circle of friends and colleagues that gave me an essential lifeline. Undeniably, these bonds were cricial to continue my research and life in Z\"urich. 


First, I would like to thank Mrs. Anne Messinger and her families for their immense kindness and humidity. I spend my first year in Z\"urich at their home at Wollishofen. They treated me like a family and reminded me that I have a second home here. 


During my stay at ETH and in the System Security group, I was fortunate to meet and become friends with some amazing people. I will start with Mridula Singh, whom I met during my masters at IIIT-Deli and also were my colleagues at Xerox research. Coming to Z\"urich, she was the only familiar face. Thanks to her and Saurav Bose, we had quite a lot of Indian food dinner sessions. All the weekend trips with them were an absolute pleasure. Special thanks to Dr. Sini\v{s}a Mateti\'c for being such a good friend and tolerating me while I was making fun of him countless times. During my Ph.D. interview, Sini\v{s}a appeared to be quite a grumpy personality. But getting to know him closely over the last five years revealed that my initial impression could not be more wrong. Thanks to David Sommer for a number of very philosophical discussions. His revolutionary ideas were breaths of fresh air, and our year-long collaboration on CoverUp during the beginning of my Ph.D. was a pleasure. Dr. Esfandiar Mohammadi is another person with whom I collaborated at the beginning of my Ph.D. Special thanks to him for mentoring me in the initial phase of my Ph.D. Special thanks to Dr. Luka Mali\v{s}a for all the conversions we had. I always found him easy to talk to about my personal struggles, which are always the most difficult conversations. I thank Karl W\"ust for such a good friend. Traveling with him and Balz to Iceland was memorable. I was always amused to see how deep knowledge he has about many other things outside computer science. Calling his craft beer knowledge encyclopedic would be an understatement. Thanks to Daniele Lani for being a good friend and an amazing officemate. Having long conversions over beers and board games at his apartment were some of the most enjoyable times I had. I am also thankful for the authentic Neapolitan pizza recipe that I got from him. Special thanks also to Dr. Thilo Weghorn for being such a good friend. The trip with him to Japan and Taiwan was an amazing experience. Thanks to Dr. Marco Guarnieri for all the conversations and attention to detail while checking draft of my papers or this thesis. Thanks to Bhargav Bhatt for a good friend and a fantastic office mate for the first two years till I moved my office. Thanks to Daina Romeo for showing me how to cook gnocchi and participating in drawing overly aggressive shouting Pokemons. Big thanks to Dr. Der-Yuan Yu for the collaboration in my earliest idea and for being such a fantastic friend. He was solely responsible for motivating me to come to the super Kondi and weight lifting session at the sports center. Thanks to Moritz and Ivan for being such amazing collaborates and friends. I thank my colleagues  Prof. Dr. Aanjhan Ranganathan, Mansoor Ahmed, Dr. Claudio Marforio, Dr. Nikolaos Karapanos, Dr. Hubert Ritzdorf, Mia Felic, Dr. Lara Schmidt, Patrick Leu, Patrick Schaller, Benjamin Rothenberger, Dr. Marc R\"oschlin, Dr. Enis Ulqinaku, Dr. AbdelRahman M. Abdou, Dr. Arthur Gervais, Dr. Srdjan Krstic, Dr. Carlos Cotrini, and Dr. Ognjen Maric for making my journey memorable. Specifically, I will remember the intense lunch discussion and various science experiments like evaluating the quality of pasta cooked in the microwave oven. Also, thanks to Christopher Signer for all the craft beer and board game sessions and for being such a kind and compassionate person. The Call of Duty gaming sessions with Chris, Daniele, Giovanni, Leonardo Nodari, and Gianluca Lain made the Covid lockdown during mid-2020 tolerable. I express my gratitude to Mrs. Barbara Pf\"andner and Mrs. Saskia Wolf for all the support and help with administrative matters during the years. 


I thank my former flatmate Clara Lovato for being a close friend. Special thanks to Kai Eva Najand for being a good friend and flatmate for the last three and half years, and tolerating my puns, and participating in the intense, heated discussion of science, architecture, and life in general. I owe a great deal to Ria Ghose and Prapti SenGupta for their constant love and support. I am truly grateful to have these two as my friends. Thanks to Dr. Priya Ghose and Dr. Anindya Basu for their friendship and kindness. The close friends I made during my master's studies at IIIT-Delhi: Sandipan Biswas, Nishan Sharma, Samir Anwar, Rohit Jain, Rohit Romley, Pankaj Sahu, Gajendra Waghmare, Ganesh Ghongane, Aniya Agarwal, Arpan Jati, Dr. Hemanta Mondal, and Amit Kr. Chauhan and my colleagues from Xerox Research: Abhishek Kumar, Raj Sharma, Kundan, Kuldeep Yadav, and Ranjeet Kumar Kanaily, all played crucial roles in shaping the person I am today.


I cannot be more thankful to my family for a loving home. My Ma, for her boundless lover and for being such a huge part in my life. My Baba, for being the biggest influence in my life and being always there for me. Most of my personal traits, love for science, painting, games, science fiction novels, comics, and countless other I inherited from him. I am grateful to my parents for raising me, trusting me, and teaching me that value of education is paramount. My paternal grandparents for their love and care. Dida, my late-grandmother, for being such an inspirational woman in my life, and dadu, my late-grandfather, who inspired and shaped my childhood. My late-maternal grandparents for being a crucial part of my childhood. Going to their place during my childhood is still vivid, and so are many holidays in distant places in India. I miss all of them dearly. You would have been proud. Chod-dida and Chor-dadu for their love and kindness. I fondly remember the weekends I spend at their place on Saturdays after the masters' entrance examination preparation classes. My cousin Prithwish Aich for being the person I always look up to.

I cannot finish this section without thanking my girlfriend, Monika Kos, for her unconditional love, kindness, compassion, and support. For standing alongside me in good times and in bad times, giving me hope and strength, especially those never-ending deadlines. She is my constant source of inspiration and joy.

\vspace{1cm}
Finally, \emph{in memorium} of my grandma, Purnima Dhar to whom I would like to dedicate this doctoral thesis. She always was my biggest champion. Her sacrifices to raise her children in the challenging  situations, her boundless love towards me teach me to be humble and inspire me to strive to be the best version of myself. Not a single day passes by when I don't miss you. You would have been proud.


\endgroup
