\section{RISC-V Keystone}

\subsection{RISC-V}
RISC-V is a modern open-source instruction set architecture (ISA). In recent years, RISC-V has sparked immense interest by industry and academia, with many software and hardware proposals. As a result, multiple open-source cores that implement various subsets of the RISC-V standard have emerged~\cite{ariane,asanovic2016rocket,riscy,asanovic2015boom}. Software-wise, RISC-V is supported by many projects, e.g., GCC, Linux, and QEMU, amongst others. RISC-V has also become a popular prototype platform for security research~\cite{weiser2019timber,costan2016sanctum,keystone}.


\subsection{Keystone TEE}

Keystone~\cite{keystone} is a TEE framework based on RISC-V that utilizes \emph{physical memory protection} or PMP to provide isolation. PMP is part of the RISC-V privilege standard~\cite{riscv2019privspec}, and it allows to specify access policies that can individually allow or deny reading, writing, and executing for a certain memory range. E.g., PMP can be used to restrict the operating system (OS) from accessing the memory of the bootloader. Every access request to a prohibited range gets trapped precisely in the core and results in a hardware exception. Keystone relies on a low-level firmware with the highest privilege, called security monitor (SM), to manage the PMP. 

The SM maintains its own memory separate from the OS and protected by a PMP entry. It also facilitates all enclave calls, e.g., it creates, runs, and destroys enclaves. The SM configures the PMP so that the OS can no longer access the enclave's private memory. Upon a context switch, the SM reconfigures the PMP to allow or block access to the enclave. E.g., during a context switch from an enclave to the OS, the SM changes the PMP configuration such that access to the enclave memory is prohibited. Conversely, on a context switch back to the enclave, the PMP gets reconfigured to allow access to enclave memory. 
Because the SM is critical for the security of any enclave and the whole system, it aims to be very minimal and lean. As such, the SM is orders of magnitudes smaller than hypervisors and operating systems (15 KLoC vs. millions LoC~\cite{torvalds2020linux,barham2003xen}). There are also efforts to create formal proofs for such a SM~\cite{lebedev2019sanctorum}. Keystone also provides extensions for cache side-channel protections using page coloring or dynamic enclave memory. 



% \subsection{Hardware Background}
% \subsubsection{RISC-V}
% RISC-V is a modern open-source instruction set architecture (ISA). In recent years, RISC-V has sparked immense interest by industry and academia, with many software and hardware proposals. As a consequence, multiple open-source cores that implement various subsets of the RISC-V standard have emerged~\cite{ariane,asanovic2016rocket,riscy,asanovic2015boom}. Software-wise, RISC-V is supported by many projects, e.g., GCC, Linux, and QEMU, amongst others. RISC-V has also become a popular prototype platform for security research~\cite{weiser2019timber,costan2016sanctum,keystone}.

% \subsubsection{Physical Memory Protection}
% Physical memory protection (PMP) is part of the RISC-V privilege standard~\cite{riscv2019privspec}. It allows specifying access policies based on a physical memory range. The access policies can individually allow or deny reading, writing, and executing for a certain memory range. For example, PMP can be used to restrict the operating system (OS) from accessing the memory of the bootloader. Every access request into a prohibited range gets trapped precisely in the core and results in a hardware exception. There are a fixed number of available PMP entries, typically 8 or 16~\cite{riscv2019privspec}, each of which allows to specify a separate memory range. Since PMP is part of the standard, it is already included in many currently available cores~\cite{riscy,asanovic2016rocket}.


